### 2024-06-18 basic-statistics.qmd
20240617 - placeholders

@@

Descriptive statistics are used to describe data.
For instance, they may be used to describe the center, spread, or shape of the data.

There are various indices of each.
Indices to describe the *center* of a variable's data include:

@@

@@

>>>>

```{r}
library("petersenlab")
library("tidyverse")
```

Descriptive statistics are used to describe data.
For instance, they may be used to describe the center, spread, or shape of the data.
There are various indices of each.

### Center {#sec-descriptiveStatisticsCenter}

Indices to describe the *center* (central tendency) of a variable's data include:

Below is R code to estimate each:

@@

### Spread {#sec-descriptiveStatisticsSpread}

@@

Below is R code to estimate each:

### Shape {#sec-descriptiveStatisticsShape}

@@

Below is R code to estimate each:

### Combination {#sec-descriptiveStatisticsCombination}

To estimate a combination of indices of center, spread, and shape of the data, you can use the following code:

```{r}
#psych::describe(mydata)

#mydata %>% 
#  summarise(across(
#      everything(),
#      .fns = list(
#        n = ~ length(na.omit(.)),
#        missingness = ~ mean(is.na(.)) * 100,
#        M = ~ mean(., na.rm = TRUE),
#        SD = ~ sd(., na.rm = TRUE),
#        min = ~ min(., na.rm = TRUE),
#        max = ~ max(., na.rm = TRUE),
#        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
#        median = ~ median(., na.rm = TRUE),
#        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
#        skewness = ~ psych::skew(., na.rm = TRUE),
#        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
#      .names = "{.col}.{.fn}")) %>%
#    pivot_longer(
#      cols = everything(),
#      names_to = c("variable","index"),
#      names_sep = "\\.") %>% 
#    pivot_wider(
#      names_from = index,
#      values_from = value)
```
